Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-08-19 docs/initial_models/paper.tex
changed the initial model for the xrb problem to initial_models/xrb/sorted_xrb.raw
initial_models/xrb/init_1d.f90 is the routine which uses the initial model file for mapping

\section{Creating the Initial Model}
The initial model returns the pressure, density, temperature, and species, denoted $p^{\init}, \rho^{\init}, T^{\init},$ and $X_k^{\init}$.  The initial model uses an iterative procedure \MarginPar{add an overview of the iterative procedure} to return a state that is both thermodynamically consistent with the {\tt MAESTRO} EOS, and in hydrostatic equilibrium,
\begin{equation}
\frac{p_r^{\init} - p_{r-1}^{\init}}{\Delta r} = \frac{\rho_r^{\init} + \rho_{r-1}^{\init}}{2}g,\label{HSE Discretization}
\end{equation}
to a user-defined tolerance.  Here is a list of which model file is used for each test problem:\MarginPar{This needs to be filled in and checked for accuracy}
\begin{eqnarray}
{\tt test2} & \rightarrow & {\tt ???} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt ???} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt ???} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt ???} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/init\_1d.f90} \nonumber
\end{eqnarray}
The initial model needs to be created at the same resolution as the base state (for single-level problems) and at the same resolution of the finest resolution base state (for multi-level plane-parallel problems).  For spherical, we force $\Delta r = \Delta x$.

>>>>

\section{Creating the Initial Model}
The initial model returns the pressure, density, temperature, and species, denoted $p^{\init}, \rho^{\init}, T^{\init},$ and $X_k^{\init}$.  The initial model uses an iterative procedure \MarginPar{add an overview of the iterative procedure} to return a state that is both thermodynamically consistent with the {\tt MAESTRO} EOS, and in hydrostatic equilibrium,
\begin{equation}
\frac{p_r^{\init} - p_{r-1}^{\init}}{\Delta r} = \frac{\rho_r^{\init} + \rho_{r-1}^{\init}}{2}g,\label{HSE Discretization}
\end{equation}
to a user-defined tolerance.  Here is a list of which model file is used for each test problem:\MarginPar{This needs to be filled in and checked for accuracy}
\begin{eqnarray}
{\tt test2} & \rightarrow & {\tt ???} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt ???} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt ???} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt ???} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/sorted\_xrb.raw} \nonumber
\end{eqnarray}
The initial model needs to be created at the same resolution as the base state (for single-level problems) and at the same resolution of the finest resolution base state (for multi-level plane-parallel problems).  For spherical, we force $\Delta r = \Delta x$.
